---
title: "Meta Analysis"
author: "Caspar J. van Lissa"
date: "September 8, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(metaforest)
library(caret)

analyzedat <- readRDS("analyzedat_imputed.RData")

nicetext <- function(x, digits = 2){
  if(x%%1==0){
    formatC(x, digits = 0, format = "f")
  } else {
    formatC(x, digits = digits, format = "f")
  }
}

```

## R Markdown

A preliminary search on Web of Science yielded 4991 articles, of which 92 met our inclusion criteria. 

A librarian wrote syntax for Web of Science, PsychInfo, and ERIC, based on meta-data from our selected articles

This resulted in 2194 relevant records. Removal of duplicates left 1786 abstracts to evaluate. 

This yielded 52 new articles, resulting in a total of 144.

Of these, `r max(analyzedat$id_study)` reported sufficient statistical information to compute a total of `r nrow(analyzedat)` effect sizes.

## Sample 2

Observed effect sizes ranged from `r nicetext(range(analyzedat[["es_correlation"]])[1])` to `r nicetext(range(analyzedat[["es_correlation"]])[2])` ($M_r = `r nicetext(mean(analyzedat[["es_correlation"]]))`$, $SD = `r nicetext(sd(analyzedat[["es_correlation"]]))`$). 

Sample sizes ranged from `r min(analyzedat[["es_n"]])` to `r max(analyzedat[["es_n"]])` participants 
 ($M_n = `r nicetext(mean(analyzedat[["es_n"]]))`$, $SD = `r nicetext(sd(analyzedat[["es_n"]]))`$). Several studies reported multiple effect sizes (`r min(table(analyzedat[["id_study"]]))` to `r max(table(analyzedat[["id_study"]]))`, with most reporting `r names(table(table(analyzedat$id_study)))[which.max(table(table(analyzedat$id_study)))]`
effect size).


## Standard meta-analysis

```{r metafor_analysis, include=FALSE}
if(FALSE){
  effect_sizes <- escalc(ri = analyzedat$es_correlation, ni = analyzedat$es_n, measure = "COR")
  
  analyzedat <- analyzedat[, -match(c("es_correlation", "es_n"), names(analyzedat))]
  analyzedat$yi <- as.numeric(effect_sizes$yi)
  analyzedat$vi <- as.numeric(effect_sizes$vi)
  
  #Conduct meta-analyses
  model.full <- rma.mv(yi, vi, random = list(~ 1 | id_study, ~ 1 | id_row), data=analyzedat) 
  model.within_null <- rma.mv(yi, vi, random = list(~ 1 | id_study, ~ 1 | id_row), sigma2=c(NA,0), data=analyzedat) 
  model.between_null <- rma.mv(yi, vi, random = list(~ 1 | id_study, ~ 1 | id_row), sigma2=c(0,NA), data=analyzedat) 
  model.both_null <- rma.mv(yi, vi, random = list(~ 1 | id_study, ~ 1 | id_row), sigma2=c(0,0), data=analyzedat) 
  
  aov_within <- anova(model.full,model.within_null) 
  aov_between <- anova(model.full,model.between_null) 
  aov_bothnull <- anova(model.full,model.both_null) 
  aov_table <- rbind(
  c(df=aov_between$p.f, aov_between$fit.stats.f[c(3:4, 1)], LRT = NA, p = NA),
  c(df=aov_within$p.r, aov_within$fit.stats.r[c(3:4, 1)], LRT = aov_within$LRT, p = aov_within$pval),
  c(df=aov_between$p.r, aov_between$fit.stats.r[c(3:4, 1)], LRT = aov_between$LRT, p = aov_between$pval),
  c(df=aov_bothnull$p.r, aov_bothnull$fit.stats.r[c(3:4, 1)], LRT = aov_bothnull$LRT, p = aov_bothnull$pval)
  )
  rownames(aov_table) <- c("Three-level model", "Within-studies variance constrained", "Between-studies variance constrained", "Both variance components constrained")
  aov_table[,-c(1,6)] <- formatC(aov_table[,-c(1,6)], digits = 2, format = "f")
  aov_table[,6] <- formatC(as.numeric(aov_table[,6]), digits = 3, format = "f")
  aov_table[1, 5:6] <-""
  write.csv(aov_table, "table_variance_components.csv")
  confints <- confint(model.full)
  save(model.full, aov_table, confints, analyzedat, file = "metafor_results.RData")
}
load("metafor_results.RData")
#CHeck convergence of variance components:
#par(mfrow=c(2,1))
#plot.profile1 <- profile(model.full, sigma2=1)
#plot.profile2 <- profile(model.full, sigma2=2)

#Write forest plot to file
#png(file="forest_plot.png",width=210,height=297, units="mm", res = 300)
#forest(model.full, xlim = c(-5.5,4), alim = c(-1, 2), xlab="Effect size (Cohen's d)", mlab="Overall estimate: ", slab = data$study, ilab=data$outcomedv,
#       ilab.xpos=c(-2), ilab.pos = c(4), cex = 0.75)
#par(cex=0.75, font=2)
#text(c(-5.5, -2.01, 2.54), 58, c("Study", "Outcome", "Cohen's d"), pos = 4)
#dev.off()

#library(extrafont)
#loadfonts()
#cairo_pdf("forest_plot.pdf", family="Helvetica", width = 8.27,height = 11.69)
#forest(model.full, xlim = c(-5.5,4), alim = c(-1, 2), xlab="Effect size (Cohen's d)", mlab="Overall estimate: ", slab = data$study, ilab=data$outcomedv, ilab.xpos=c(-2), ilab.pos = c(4,4,4), cex = 0.75)
#par(cex=0.75, font=2)
#text(c(-5.5, -2.01, 2.54), 58, c("Study", "Outcome", "Cohen's d"), pos = c(4,4,4))
#dev.off()
#embed_fonts("forest_plot.pdf", outfile="forest_plot.pdf")

```

```{r publication_bias, echo=FALSE, include=FALSE}

beggs <- regtest(x = analyzedat$yi, vi = analyzedat$vi, predictor = "vi")
beggs


#file drawer analysis (fail and safe)
fsn <- fsn(yi = analyzedat$yi, vi = analyzedat$vi, 
           #data = , 
           #subset = c(domain, hit2Grouped), 
           )
```

## Slide with Bullets

```{r funnel_plot, echo=FALSE, fig.cap="A caption", out.width = '100%'}
funnel(model.full, xlab = "Residual Value", back = "white") #funnel plot for qualitative evaluation publication bias
```
